The {TestIdeals} package for \emph{Macaulay2}

### 2019-01-19 Fsing/TestIdealsPaper/TestIdeals.tex
Fixed couple of typos found by referee

\begin{document}
\title{The  {TestIdeals} package for \emph{Macaulay2}}
\author[Alberto F.\ Boix et at.]{Alberto F.\ Boix}
\address{Department of Mathematics, Ben-Gurion University of the Negev, Beer-Sheva 8410501, Israel}
\email{fernanal@post.bgu.ac.il}
\thanks{A.F.~Boix was supported by Israel Science Foundation (grant No. 844/14) and Spanish Ministerio de Econom\'ia y Competitividad MTM2016-7881-P}

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/2[x,y,z];
i2 : f = x^3+y^2*z+y*z^2;
i3 : frobeniusPower( 1/2, ideal f )
o3 = ideal (x, y , z )
o3 : Ideal of R
i4 : u=f^3;
i5 : frobeniusPower( 1/4, ideal u )
o6 = ideal (x, y , z )
o6 : Ideal of R
i7 : ((HSLGModule(1, f))#3) + 1
o7 : 2
\end{MyVerbatim}
}\medskip

This shows that this elliptic curve has level $2,$ hence it is supersingular. The next example
shows a non--ordinary hyperelliptic curve of genus $2$ with level $2.$

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/11[x,y,z];
i2 : f = y^2*z^3-x^5-2*z^5;
i3 : frobeniusPower( 1/11, ideal f )
             2        3
o3 = ideal (z , x*z, x )
o3 : Ideal of R
i4 : u=f^{121-1};
i5 : frobeniusPower( 1/121, ideal u )
             2        3
o6 = ideal (z , x*z, x )
o6 : Ideal of R
i7 : ((HSLGModule(1, f))#3) + 1
o7 : 2
\end{MyVerbatim}
}\medskip

>>>>

\begin{document}
\title{The  {TestIdeals} package for \emph{Macaulay2}}
\author[Alberto F.\ Boix et al.]{Alberto F.\ Boix}
\address{Department of Mathematics, Ben-Gurion University of the Negev, Beer-Sheva 8410501, Israel}
\email{fernanal@post.bgu.ac.il}
\thanks{A.F.~Boix was supported by Israel Science Foundation (grant No. 844/14) and Spanish Ministerio de Econom\'ia y Competitividad MTM2016-7881-P}

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/2[x,y,z];
i2 : f = x^3+y^2*z+y*z^2;
i3 : frobeniusPower( 1/2, ideal f )
o3 = ideal (x, y, z)
o3 : Ideal of R
i4 : u=f^3;
i5 : frobeniusPower( 1/4, ideal u )
o6 = ideal (x, y, z)
o6 : Ideal of R
i7 : ((HSLGModule(1, f))#3) + 1
o7 : 2
\end{MyVerbatim}
}\medskip

This shows that this elliptic curve has level $2,$ hence it is supersingular. The next example
shows a non-ordinary hyperelliptic curve of genus $2$ with level $2$.

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/11[x,y,z];
i2 : f = y^2*z^3-x^5-2*z^5;
i3 : frobeniusPower( 1/11, ideal f )
o3 = ideal 1
o3 : Ideal of R
i4 : u = f^(121-1);
i5 : frobeniusPower( 1/121, ideal u )
             2        3
o6 = ideal (z , x*z, x )
o6 : Ideal of R
i7 : ((HSLGModule(1, f))#3) + 1
o7 : 2
\end{MyVerbatim}
}\medskip
